---
title: "Technical Appendix"
author: Qianhui Guo, Hannah Khuong
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

```{r echo = FALSE }
##Program's Header##

# title: Technical Appendix
# author: QianhuiGuo, Hannah Khuong
# date: February 17, 2019
# output:
#   html_notebook:
#     toc: true
#     toc_depth: 4


# title: "Technical Appendix"
# author: "QIANHUI GUO, Hannah Khuong"
# date: "`r format(Sys.time(), '%B %d, %Y')`"
# output: html_notebook


```

#Commented Header  

```{r}
# Course: BUAN 5210
# Title: Technical Appendix
# Purpose: Observe the effectiveness of in-store promotions and advertisements based on Basic EDA and detailed EDA
# Date: Feb 17th, 2019
# Author: Qianhui Guo, Hannah Khuong
```


#Clear Working Environment 

```{r message = FALSE, result = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```

```{r message = FALSE, warning=FALSE }
# load packages
library(tidyverse)
library(GGally)
library(gridExtra)
library(readr)
library(here)
library(janitor)
library(stringr)
library(knitr)
library(Hmisc)
library(kableExtra)
library(htmlTable)
library(car)
library(sjPlot)
```

#Load data and prepare for EDA

```{r message = FALSE}
product <- read_csv(here("mtp_product_data.csv"))
sales <- read_csv(here("mtp_sales_data.csv"))

# view data
str(product)
str(sales)
```


```{r message = FALSE}
#Data Manipulation

# match UPC format
upc_pattern <- "([0][1-3][. -][1-8]{2}[0]{3}[. -][0-9]{5})" # define pattern for UPC
product <- product %>%
  mutate(
    UPC =str_extract_all(UPC,upc_pattern),    # find out the same part 
    UPC = str_replace_all(UPC,'-','.')     ) %>%  # replace '-'with '.'
  select(-package) # package is useless in this moment, so we don't take it into account


# left join 
tidy_table <-left_join(sales,product) %>%
  mutate(
# rename the category within the ad
    ad = case_when(
      ad == 'A' ~ 'Big Ads',
      ad == 'B' ~ 'Medium/Small Ads',
      ad == "NONE" ~ 'No Ads'
    ),
# convert character into factor
    iri_key = as.factor(iri_key),
    ad = as.factor(ad),
    promo = as.factor(promo),
    flavor = as.factor(flavor),
    
# calculate total price for each purchase
    revenue = units * price,

# seperate the brand into producer and product name
  producer = ifelse(str_detect(brand,"GENERAL MILLS"),"GENERAL MILLS",
            ifelse(str_detect(brand,"KELLOGGS"),"KELLOGGS",
            ifelse(str_detect(brand,"POST"),"POST",NA))),
  producer = as.factor(producer)
  ) %>%
# abandon store number as well 
  select(-iri_key,-brand) 

#Rename promo level
levels(tidy_table$promo) <- c("No", "Yes")

```


#Basic EDA 

##Univariate Analysis

### Non-graphical Analysis

```{r}
# descriptive statistics
summary(tidy_table)
```

+ Observation from the data: 
    - There are 5 numerical variables and 4 factor variables. 
    - price and revenue are right skewed.
    - REGULAR flavor is sold the most.
    - KELLOGGS's product is sold the most, about six times the least-sold product (POST).
    - In most cases, there are no promo or advertisement (20% of the time, items are sold with promotions).

```{r}
#Create function for frequency tables 
count_table <- function(x,colname){
   x = enquo(x)
   kable(
    tidy_table %>%
      tabyl(!!x) %>%
      adorn_totals()%>%
      adorn_pct_formatting(digits = 0 ),
      digits = 2,
      format = "html",
      align = c("l","c","c"),
      col.names = c(colname,"Count","Total")
    )%>%
  kable_styling(full_width = F)}

#Make count tables for univariate variables 
count_table(promo,"Promotion")
count_table(ad,"Advertisement")
count_table(flavor,"Flavor")
count_table(producer,"Producer")
```



    
### Graphical Analysis

####Categorical Variables   

```{r}
#Functions for graphs 

#Count bargraph 
count_bargraph <- function(x) {
  x + geom_bar(position = "dodge") +
    theme_bw() + 
    theme(panel.border = element_blank(), 
                       panel.grid.major = element_blank(),
                       panel.grid.minor = element_blank()) + 
    labs(y ="Count")
}

#Count histogram
count_hist<- function(x){
  x + geom_histogram(bins = 52)+
    theme_bw() + 
    theme(panel.border = element_blank(), 
                       panel.grid.major = element_blank(),
                       panel.grid.minor = element_blank()) + 
    labs(y ="Count")
}

#Make bar chart with values
bar_chart <- function(x){ x +
  geom_bar(stat = "identity",position = "dodge") + theme_bw() + 
  theme(panel.border = element_blank(), 
                       panel.grid.major = element_blank(),
                       panel.grid.minor = element_blank()) 
  
}

```

```{r fig.height= 10}
grid.arrange(
  count_bargraph(ggplot(tidy_table, aes(promo))) + 
                          xlab("Promotion"),
  count_bargraph(ggplot(tidy_table, aes(ad))) + 
                          xlab("Advertisement"),
  count_bargraph(ggplot(tidy_table, aes(flavor))) + 
                          xlab("Flavor")+
                          theme(axis.text.x = element_text(angle=60, hjust=1)), 
  count_bargraph(ggplot(tidy_table, aes(producer))) + 
                          xlab("Producer") +
                          theme(axis.text.x = element_text(angle=60, hjust=1)),
 
  nrow = 2)
```

+ Findings from the bar chart: 
    - In most of the time, there is no ads or promotions on selling cereal. 
    - Regular flavor is the most popular flavor.
    - Kelloggs has more order than others. 

####Continuous Variable  

```{r}
# create histograms of continuous variables 
grid.arrange(
  count_hist(ggplot(tidy_table, aes(week))),
  count_hist(ggplot(tidy_table, aes(price))),
  count_hist(ggplot(tidy_table, aes(units))), 
  count_hist(ggplot(tidy_table, aes(revenue))),
  count_hist(ggplot(tidy_table, aes(volume))),
nrow = 2
)
```

+ Obeservations of the data: 
    - There are fewer sales at greater number of units and higher total price. 
    - The price is nearly normal disrtibuted, and most of products sold at the price around $3.75. 

##Multi-variate analysis 

###Non-graphical 

####Categorical variables
```{r}
#Function for table
freq_table <- function(x, y, name, cols){
   x = enquo(x)
   y = enquo(y)
   kable(
    tidy_table %>%
      tabyl(!!x, !!y) %>%
      adorn_totals(where = c('row','col')) %>%
      adorn_percentages(denominator = "all")%>%
      adorn_pct_formatting(digits = 0 ),
      digits = 2,
      format = "html",
      align = c("l","c","c","c","c"),
      caption = name,
      col.names = cols
    )%>%
  kable_styling(full_width = F)
}
```

#####The relationship of advertising/promotion and different producers

```{r }
# Create frequency tables (by percentage)

#Producer - Ads 
freq_table(producer, ad, "Percent of Sales under Advertisement for Different Producers", 
           c("Producer", "Big Ads", "Medium/Small Ads", "No Ads", "Total"))

#Producer - Promotion 
freq_table(producer, promo,
           "Percent of Sales under Promotion for Different Producers", 
           c('Producer','No Promotion','With Promotion','Total'))


```

+ Findings from the table:    
    - KELLOGGS has the biggest sale among the producers no matter whether there is any advertisement or promotion.  
    - POST is the least popular among the producers no matter whether there is any advertisement or promotion.  
    - In overall, big advertisement leads to more sales than small/ medium advertisement among the products from KELLOGGS and GENERAL MILLS. 
    
#####The relationship of advertising/promotion and different flavors

```{r}
# Create frequency tables (by percentage)

#Flavor - Advertisement 
freq_table(flavor, ad, "Percent of Sales under Advertisement for Different Flavors", 
           c("Flavor", "Big Ads", "Medium/Small Ads", "No Ads", "Total"))

#Flavor - Promotion 
freq_table(flavor, promo, "Percent of Sales under Promotion for Different Flavors",
           c('Flavor','No Promotion','With Promotion','Total'))

```

+ Findings from the table:    
    - Regular flavor and toasted flavor dominate the sale whether there is a promotion or advertising or not.
    - Big advertisement has no less sale than medium/small advertisement in different flavors.

    
#####The relationship between promotion and advertising

```{r}
#Frequency Table 

#Advertising - Promotion 
freq_table(ad, promo,"Percent of Sales under Promotion and Advertising" ,c("Advertisement",'No Promotion','With Promotion','Total')) 

```

+ Findings from the table:
    - With an advertisement in the same time, promition can increase sales by 1%.
    - Whether there's a promotion or not, big advertisements lead to more sale than medium/small advertisements by 1%. 
    
###Graphical Analysis

####Categorical variable 

Create Heatmap to visualize number of sales
```{r}
#Function for heatmap
 heat_map <- function (x, y,y_title,x_title){
   x<-enquo(x)
   y<-enquo(y)
   
   
   tidy_table %>%
     group_by(!!x,!!y) %>%
     summarise(count = n())  %>%
     ggplot(aes(!!x,!!y)) +
     geom_tile(aes(fill = -count))+
     ylab(y_title) + xlab(x_title)+
     scale_fill_continuous(guide = guide_legend(title = "Count"))
     
 }
```

```{r fig.width= 12}
grid.arrange(
heat_map(producer,promo,"Promotion","Producer"),
heat_map(producer,ad,"advertisement","Producer"),
heat_map(flavor,promo,"Promotion","Flavor"),
heat_map(flavor,ad,"Advertisement","Flavor"),
heat_map(ad,promo,"Promotion","Advertisement"),
nrow=3)
```

+ Findings from the Heatmap:     
    - Kelloggs dominate the sale in the cereal market.
    - In most of time, there is no ads or promotion in the market.In the meanwhile, regular flavor is the most popular flavor among customers. 

####Continuous Variables 

#####Correlations  

```{r message = FALSE, warning = FALSE }
# find out correlation between quantative via ggpairs()
tidy_table %>% 
  select(units,price,revenue,volume, week) %>%  # select numerical variables 
  ggpairs()
```

+ Findings: 
    - volume and price have a high correlation between each other.
    - price and total price has long right tail. 
    - volume and price are nearly normal distributed


#####Scatterplots 

```{r}
# Make Scatter-plot for Volume - Price
tidy_table %>%
  ggplot(aes(x = volume, y = price)) +
  geom_point() +
  geom_smooth(method =  "lm", se = FALSE)
```

+ Finding: 
    - More volume of cereal requires higher price, which is totally make sense. 

####Categorical and Continuous variables

```{r fig.width = 10}
grid.arrange(
count_bargraph(ggplot(tidy_table, aes(producer, fill = ad))) + 
                        xlab("Producer"),
count_bargraph(ggplot(tidy_table, aes(producer, fill = promo))) + 
                        xlab("Producer"),ncol=2)
```

+ Obeservation of the data
    - Whether there are any advertisement or promotion or not, KELLOGGS sales much more product than the other producer

#Detailed EDA

## Which flavor is more profitable in differnet companies?


```{r}
bar_chart(
  tidy_table %>%
    select(producer,flavor,revenue) %>%
    group_by(producer, flavor) %>%
    summarise(
      revenue = sum(revenue)
    )%>%
  ggplot(aes(x = producer, y = revenue, fill = flavor)))

```

+ Findings: 
    - POST producer only has one flavor of cereal in the market. But both GENERAL MILLS and KELLOGGS have 4 flavor in their markets. 
    - Regular flavor is the most profitable flavor in the market.
    - The reason why KELLOGGS earns more than GENERAL MILLS is that the regular flavor from KELLOGGS is much more popular than the other. 
    - GENERAL MILLS is less competitive in terms of regular flavor.
    - Toasted flavor is the most sold among General Mills flavors. 
    - Cinnamon Toast flavor is General Mills company's unique flavor compared to Post and Kelloggs. 
    
##On what flavor does promotion/advertisement show the best effects in GENERAL MILLS?  


###Promotion Premium 

```{r}
#Make functions 
producer_premium <- function(x, y, z, title, produc, math){
  x <- enquo(x)
  y <- enquo(y)
  z <- enquo(z)
  table<- tidy_table%>% 
  filter(producer == produc )%>%
  select(!!z, !!y,!!x) %>%
  group_by(!!z,!!x) %>%
  summarise_all(math) %>% # calculte the weekly total 
  spread(!!z,!!y) 
  
  table[is.na(table)] <- 0 
  
  table%>%
  mutate(promotion_premium = Yes - No)%>%
  ggplot( aes(x = !!x, y = promotion_premium, fill =!!x)) + 
    geom_bar(stat= "identity") + 
    ggtitle(title) +
    theme_bw() + 
    theme(
    panel.border = element_blank(), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())  + ylab("Total Promotion Premium")+
    guides(fill=FALSE) 
  
}
```

####which flavor in General Mills sale more with promotions? 


```{r}
producer_premium(flavor, units, promo, "The total promotion premium on units sold varies by flavors", "GENERAL MILLS", median)
```

* People buy more cereal units if there is a promotion, especially for cinnamon toast and cocoa flavor. 


#### which flavor in General Mills is more profitable with promotion?

```{r}

producer_premium(flavor, revenue, promo, "The Total Promotion Premium on Revenue varies by Flavors", "GENERAL MILLS", mean)

```

* Promotion is not always helpful in all flavor
    + promotions on cinnamon toast and cocoa flavor increase revenue for the company. 
    + General Mills should stop offering any promotions on toasted flavor as it accounts for a loss of the company. 
    
###Revenue/Units sold and Flavors 

```{r}

bar_chart_math <- function(x, y, z, math, produc, ytitle, guide){ 
  x <- enquo(x)
  y <- enquo(y)
  z <- enquo(z)
  tidy_table %>% 
    filter(producer == produc) %>%
  ggplot(aes(x = reorder(!!x, !!y), y = !!y, fill = !!z))+
  stat_summary( fun.y= math, geom="bar",position = "dodge") + theme_bw() + ylab(ytitle)+xlab("Flavors")+
  theme(panel.border = element_blank(), 
                       panel.grid.major = element_blank(),
                       panel.grid.minor = element_blank()) +
    scale_fill_brewer(palette = "Blues",guide = guide_legend(title = guide))
   
  
}
grid.arrange(

bar_chart_math(flavor, revenue, promo, "mean", "GENERAL MILLS", "Revenue", "Promotion")+ 
  stat_summary(geom= "errorbar", fun.data = "mean_cl_normal", width = 0.4, position = position_dodge(0.9)) ,

bar_chart_math(flavor, units, promo, "median", "GENERAL MILLS", "Units sold", "Promotion"),nrow = 2, top = "Promotion on Revenue and Units sold")


grid.arrange(
bar_chart_math(flavor, revenue, ad, "mean", "GENERAL MILLS", "Revenue", "Advertisement")+ 
  stat_summary(geom= "errorbar", fun.data = "mean_cl_normal", width = 0.4, position = position_dodge(0.9)),

bar_chart_math(flavor, units, ad, "median", "GENERAL MILLS", "Units sold", "Advertisement"), nrow = 2, 
top = "Advertisement on Revenue and Units sold")

#Statistical testing 
GM <- tidy_table%>%filter(producer == "GENERAL MILLS") 
#Promotion
summary(aov(revenue[flavor == "TOASTED"]~promo[flavor == "TOASTED"], data = GM))
summary(aov(revenue[flavor == "COCOA"]~promo[flavor == "COCOA"], data = GM))
summary(aov(revenue[flavor == "CINNAMON TOAST"]~promo[flavor == "CINNAMON TOAST"], data = GM))
summary(aov(revenue[flavor == "REGULAR"]~promo[flavor == "REGULAR"], data = GM))

#Ads 
summary(aov(revenue[flavor == "TOASTED"]~ad[flavor == "TOASTED"], data = GM))
summary(aov(revenue[flavor == "COCOA"]~ad[flavor == "COCOA"], data = GM))
summary(aov(revenue[flavor == "CINNAMON TOAST"]~ad[flavor == "CINNAMON TOAST"], data = GM))
summary(aov(revenue[flavor == "REGULAR"]~ad[flavor == "REGULAR"], data = GM))


```

* Overall, Advertisement lead to an obvious increase in sale in all flavors for General Mills.

* Ads have different effect on different flavor.
    + Ads doesn't have a significant effect on the revenue of regular flavor, but on its sale instead. 
    + we suggest not to provide regular flavor with ads. 
    + As for Cocoa flavor, Medium/small ads lead to more revenue. While as for cinnamon toast and toasted flavor, we suggest offer big ads as it brings highest revenue among all the advertising strategies. 
    
* From Statistical analysis: 

    + We can conclude that there is a relationship between promotion and revenue for cocoa flavor and cinnamon toast flavor, statistically significant at the 5% level of significance. While as for regular flavor, there is no relationship between promotion and revenue. 
    + In most flavor, there is no relationship between ads and revenue except cocoa flavor. The relationship for cocoa flavor is statistically significant at 5% level of significance.
    
```{r fig.height = 7, fig.width=5 }

grid.arrange(
bar_chart_math(flavor, revenue, promo, "mean", "GENERAL MILLS", "Revenue", "Promotion")+ 
  stat_summary(geom= "errorbar", fun.data = "mean_cl_normal", width = 0.4, position = position_dodge(0.9)),

bar_chart_math(flavor, revenue, promo, "sum", "GENERAL MILLS", "Revenue","Promotion"), nrow = 2)

```

```{r fig.height = 4, fig.width=4 }
b<- arrangeGrob(
bar_chart_math(flavor, revenue, promo, "mean", "GENERAL MILLS", "Revenue", "Promotion")+ 
  stat_summary(geom= "errorbar", fun.data = "mean_cl_normal", width = 0.4, position = position_dodge(0.9)),
bar_chart_math(flavor, revenue, promo, "sum", "GENERAL MILLS", "Total Revenue","Promotion"), nrow = 2, 
top = "Figure 2. Cocoa Flavor Generates the Lowest Revenue\nbut Yields the highest Promotion Premium")
ggsave("flavor.png", b)

```



##At a same time, how does General Mills cereal sales look like, with and without promotions or advertisement? 

* People buy more cereal units if there is a promotion. 

* The effect of ads can be seen clearly.
    + Without ads, number os units sold in each check-out vacillate under 10 units.
    + With ads, people tend to buy more units and at higher total price per check-out. 
    + Big ads does not seem to be as effective in increasing units sale and total check-out price like medium and small ads. 

###Promotion


```{r fig.width = 8, fig.height = 8}

#Create graph function 

line_graph<- function(x, y, z,math){
  x <- enquo(x)
  y <- enquo(y)
  z <- enquo(z)
  tidy_table %>% 
    filter(producer == "GENERAL MILLS") %>%
  ggplot(aes(x = !!x, y = !!y, color = !!z))+ 
    stat_summary(fun.y = math , geom = "point") + stat_summary(fun.y = math, geom = "line") +
    theme_bw() + theme(panel.border = element_blank())

}
grid.arrange(
#Graph time-series of units sold
line_graph(week, units, promo, "median" ), #Promotion


#Graph time-series of total revenue per sale
line_graph(week,revenue,promo, "mean"),#Promotion
nrow = 2)

```

###Advertisement
```{r fig.width = 8, fig.height = 8}
grid.arrange(
#Graph time-series of units sold
line_graph(week, units,  ad,"median"), #Ads 

#Graph time-series of total revenue per sale
line_graph(week, revenue, ad, "mean"), 
nrow = 2)
```

###Statitical Testing 

####Revenue

```{r}
#Revenue
#Difference in revenue in with or without promotion program 
t.test(tidy_table$revenue ~ tidy_table$promo)

#Difference in revenue in different advertisement program 
summary(aov(tidy_table$revenue ~ tidy_table$ad))

par(mfrow = c(1,2))
boxplot(tidy_table$revenue ~ tidy_table$promo)
boxplot(tidy_table$revenue ~ tidy_table$ad)
```

####Units sold 

```{r}
#Units sold
#Difference in units sold in with or without promotion program 
t.test(tidy_table$units ~ tidy_table$promo)

#Difference in units sold in different advertisement program 
summary(aov(tidy_table$units ~ tidy_table$ad))

par(mfrow = c(1,2))
boxplot(tidy_table$units ~ tidy_table$promo)
boxplot(tidy_table$units ~ tidy_table$ad)

```

* We can conclude that the differences in terms of revenue and units sold between promotion conditions and advertisement groups are highly statistically significant. 


### How is the interaction of advertisement and promotion affecting units sold and revenue? 



```{r fig.height = 4, fig.width=4, message = FALSE, warning=FALSE}


promotion_ad <- function(x,ylab,title, math) {

  x <- enquo(x)
  GM_table %>%
  group_by(promo,ad) %>%
  ggplot(aes(x =promo, y = !!x,fill=promo)) +
    stat_summary(geom="bar", fun.y = math) + 
  facet_wrap(.~ad) +
  ylab(ylab)+
  xlab("Promotion") +
  ggtitle(title) + 
  theme_bw() + 
  theme(
    panel.border = element_blank(), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) +
    scale_fill_brewer(palette = "Blues",guide = guide_legend(title = "Promotions"))
    
}

GM_table <- tidy_table %>%
  filter(producer == "GENERAL MILLS") %>% 
  select(week,promo,units,ad,revenue) %>%
  group_by(week,promo,ad) %>%
  summarise_all(mean) 



GM_table[is.na(GM_table)] <- 0 


g <- arrangeGrob(
promotion_ad(revenue,"Mean Revenue (Mean)"," ", mean)+ stat_summary(geom = "errorbar", fun.data = "mean_cl_normal", width=0.1),
promotion_ad(units,"Quantity (Median)"," ", median) ,
nrow =2, top = "Figure 1. Advertisements and Promotions have different effects\n on Revenue and Quantity Sold"
)

ggsave("promo-ad-interaction.png", g)

```

```{r fig.height = 7, fig.width = 5}
grid.arrange(
promotion_ad(revenue,"Mean Revenue (Mean)","Revenue varies by promotions and Ads", mean)+ stat_summary(geom = "errorbar", fun.data = "mean_cl_normal", width=0.1),
promotion_ad(units,"Quantity (Median)","Quantity varies by promotions and Ads", median)  ,
nrow =2
)
```


####Statistical Testing

* Promotions stimulate customers to buy more products each time

* Promotions lead to a slight increase in revenue 

* The effect of Medium/Small Ads are worse than the others in both quantity and revenue without a promotion.But with a promotion, Meium/Small Ads lead to more sale each time than that without ads.


```{r}
#Statistical Testing  - two-way ANOVA

#Revenue and ad-promo
summary(aov(revenue ~ ad + promo, data = GM))

```

* Different types of dvertisement and promotion programs do not affect revenue for GENERAL MILLS. 

```{r}
#Revenue and ad-promo
summary(aov(revenue ~ promo, data = GM))
summary(aov(units ~ ad + promo, data = GM))
```

* Different types of dvertisement and promotion programs do affect revenue for GENERAL MILL. 
    + The difference between promotion programs is significant at 0% level. 
    + The difference between promotion programs is significant at 0.01% level. 

##Is promotion premium different among the three companies? 

###Revenue 

```{r}
#

premium <- function(x, y, z, title){
  x <- enquo(x)
  y <- enquo(y)
  z <- enquo(z)

  table<- tidy_table%>% 
  select(week, !!z, !!y,!!x) %>%
 
     group_by(week,!!z,!!x) %>%
  summarise_all(mean) %>% 
  spread(!!z,!!y) 
  
  table[is.na(table)] <- 0 
  
  table%>%
  mutate(promotion_premium = Yes - No)%>%
  group_by(!!x)%>%
  
  ggplot(aes(x = !!x, y = promotion_premium, fill = !!x)) +
    stat_summary(geom ="bar", fun.y = "sum") +
    ggtitle(title) + ylab("Total Premium") +
  theme_bw() + 
  theme(
    panel.border = element_blank(), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) 
  
}
grid.arrange(
premium(producer, revenue, promo, "The total promotion premium in terms of Revenue vary by producer"),
premium(producer, units, promo, "The total promotion premium in terms of Units sold vary by producer"),nrow = 2)

```

* Promotion has much effect on revenue for Kelloggs, but not for General Mills. 
  + With promotion, General Mills has a significant increase in its units sold, but its revenue increase only a little bit for the whole year.
  + While promoton has a great positive effect on Kelloggs on both sale and revenue. 

#Build Multiple-Linear Regression Model 

```{r}
model <- lm(revenue ~ producer + ad + promo + units + flavor + volume + ad*promo,data = tidy_table)
summary(model)
```

##Model diagnosis 

```{r fig.height=8}
# plot residuals to check for patterns
par(mfrow = c(2,3))
plot(tidy_table$producer,model$residuals)
plot(tidy_table$flavor,model$residuals)
plot(tidy_table$units,model$residuals)
plot(tidy_table$ad,model$residuals)
plot(tidy_table$volume,model$residuals)
```

```{r}
model_diag <- plot_model(model, type ="diag")
model_diag[1]
model_diag[2]
model_diag[3]
model_diag[4]
```

**Conclusion**

* This model satisfy the basic assumption of multiple linear regression model to be unbiased. 

* However, this model is heteroscedasticity. As x value increases, the residuals also increases. 

##Table for estimators in multi-linear regression model 
```{r}
# Pull out the coefficients and confidence interval for table and graph
coefficent <- summary(model)$coefficients # get coefficients and related stats
coe_CI <- as.data.frame(cbind(coefficent[-1, ], confint(model)[-1, ])) # find and bind CI, remove Intercept 

# Rename results data frame
names(coe_CI) <- c("estimate", "se", "t", "pval","low_CI","high_CI") 

htmlTable(round(coe_CI[order(coe_CI$pval, decreasing = FALSE),],3))
```

**Comments**

* The relationship of Revenue with Promotion, units, volume, producer, No ads, regular and toasted flavor are all statistical significant at 1% level of significance.

* The relationship of revenue with fruit flavor is statistical significant at 5% level of significance. 

* Medium/Small Ads, No Ads, and Cocoa flavor does not have significant relationship with revenue.
     
##Plot estimated coefficients of relationship between revenue and independent variables

```{r}
ggplot(coe_CI,aes(x = estimate, y = reorder(row.names(coe_CI),desc(pval)))) +
  geom_point() +
  ylab("Variable") + 
   xlab("Coefficient with Confidence Interval") +
  theme_bw()+ 
  geom_segment(aes(yend = reorder(row.names(coe_CI),desc(pval))),
                xend = coe_CI$high_CI,color= "Blue") +
  geom_segment(aes(yend = reorder(row.names(coe_CI),desc(pval))),
                xend = coe_CI$low_CI,color= "Blue") + 
  geom_vline(xintercept = 0, color= "Red")

```

* Controlling for flavors, package volumes, units sold and advertisement, sales with promotion on average give companies $5.18 less than sales without promotion. 

* Controlling for flavors, package volumes, units sold and promotion, sales with no advertisement on average give companies $5.45 more than than sales with Big Ads.

* Given that the price of a cereal unit is around $2 to $3, this gain or loss on a transaction is economically significant. 

#Summary of results 

**Buying pattern**: 

* Most of the time, customers purchased cereals without advertisement (88%) or without promotions (79%).

* Seventy-nine percent (79%) of the time, customers purchased cereals without any advertisement and promotions. 

**Flavor analysis**: 

* Regular flavor is the best-seller on the market, while this is not a well-sold flavor for General Mills. This flavor also goes on discount the most frequently. 

* Toasted flavor is General Mills best seller, and it is also the best-selling company for Toasted flavor in the market. This flavor is on discount the second-most frequently. 
    + Cinnamon Toasted flavor is a unique flavor General Mills offers, which also generate good revenue (higher than all revenue from POST).
  
* The biggest competitor for General Mills is Kellogg and their strength is Regular flavor cereals.

**Compare sales with Promotions/Advertisement and without Promotions/Advertisement**: 

* Promotion and advertisement make number of cereal units sold per week significantly higher than number of units sold without promotion or advertisement. 

* Promotion and advertisement also makes revenue per week statistically significantly higher than revenue without promotion or advertisement. However, there are more fluctuation in the advertisement condition versus no advertisement sales. 

**Multi-linear Regression Model**: 

* From our multi-linear regression model, promotion can make companies lose $5.18 on a sale. Big advertisements make companies lose $5.45 on a sale, compared to sales without any advertisement Given that the price of a cereal unit is around $2 to $3, this gain or loss on a transaction is economically significant. 

#Save File
```{r}
# Save the rds file so I can reuse anything from this file in another file
save.image("mid.RData")

# recover using load()
load("mid.RData")
```
